---
title: "Choosing reasonable amounts of heterogeneity for our theoretical examples and the Shiny app"
output: html_document
---

For the theoretical analyses and the Shiny App, we had to select reasonable values for the
(residual) between study variances $\tau^2$. To reflect $\tau^2$-estimates in
Psychology, we based our choice of $\tau^2$ on a dataset by van [Erp et al. (2017)](https://openpsychologydata.metajnl.com/articles/jopd.33) 
which can be accessed via this [link](https://doi.org/10.5334/jopd.33.s2).
The dataset contains 705 heterogeneity estimates from 61 meta-analyses published in Psychological Bulletin
between 1990 and 2013. 
As all examples in our paper use standardized mean differences as effect size, 
we filtered the this dataset for $\tau^2$-estimates that came from a meta-analysis
in the effect size was a standardized mean difference. 

The following code details how we obtained the first, second and third quantile of the
observed tau2 estimates. 

```{r, }
# Import the data
url <- "https://doi.org/10.5334/jopd.33.s2"
file_name <- "vanErp.xlsx"
file_path <-  getwd()
destfile <- paste0(file_path,"/", file_name, sep = "")
download.file(url = url, destfile = destfile, mode = "wb")
data <- readxl::read_excel(destfile)

```



```{r}
# we are interested only in tau2 estimates where SMD were the effect sizes, however,
# the dataset also contains information from meta-analyses with different effect sizes
unique(data$`Type of ES`)

# select SMD effect sizes only
data.SMD <- subset(data, `Type of ES` %in% 
                  c("Cohen's d" , "Hedges' g", "Corrected Cohen's d" ,"Weighted Cohen's d"))

# show the histogram of tau2 estimates
hist(data.SMD$`tau^2`, xlab = "tau2", main = "Histogram tau2 estimates from meta-analyses
     using standardized mean differences as effect size")


# obtain the quantiles
Q1 <- quantile(data.SMD$`tau^2`,  0.25, na.rm = TRUE)
Q2 <- quantile(data.SMD$`tau^2`,  0.5, na.rm = TRUE)
Q3 <- quantile(data.SMD$`tau^2`,  0.75, na.rm = TRUE)

```

Of the `r nrow(subset(data, !is.na(data[["tau^2"]])))` $\tau^2$-estimates in the data, only `r nrow(data.SMD) ` belong to meta-analyses using standardized mean differences. The frequency of $\tau^2$-estimates is shown in the histogram.
The $\tau^2$ distribution yields the following quantiles: 

- Q1 = `r Q1`
- Q2 = `r Q2`
- Q3 = `r Q3`.


As a side note, all calculations in the paper and in the app can also be done by specifying
certain (residual) $I^2$ values instead of specifying $\tau^2$.
